Update on Google mobility reports on Austria

### 2021-01-08 _post/2020-06-08-update-on-mobility-patterns/update-on-mobility-patterns.Rmd
post update mobility reports; plot bkg color linked to css bkgd

# Setup
<details closed> 
<summary>Load packages</summary> 
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(extrafont)
loadfonts(device = "win", quiet = T)
library(hrbrthemes)
hrbrthemes::update_geom_font_defaults(family="Roboto Condensed")
# hrbrthemes::update_geom_font_defaults(family="Plex Sans")
library(scales)
library(grid)
library(knitr)
library(geofacet)
library(paletteer)
library(ggtext)
library(glue)
library(gt)
```
</details>

@@

options(width=180, dplyr.width = 150)
```
</details>

@@

```{r eval=FALSE, fig.height=6, include=FALSE}
plot_park <- df_temp_mobility %>% 
  ggplot()+
  labs(x="daily average temperature",
       y="change to pre-Covid19 baseline period",
       title="Changes in presences in parks, Covid19 lockdown measures and weather",
       subtitle="Average temperature of state's captial used",
       caption=c("data: NOAA, Google Mobility Reports", "graph: Roland Schmidt | @zoowalk | www.werk.statt.code"))+
  geom_smooth(aes(y=google.value,
                  x=tavg),
              size=0.5,
              color="black",
              method='lm', 
              formula= y~x)+
  geom_point(aes(y=google.value,
                 x=tavg,
                 color=day.indicator),
             size=.5)+
  # geom_smooth(aes(y=google.value,
                  # x=tavg))+
  scale_color_manual(values=c("business day"="steelblue",
                                        "public holiday"="green3",
                                        "weekend"="orange"))+
  scale_y_continuous(labels=scales::label_percent(accuracy = 1,
                                                            scale=1),
                               limits=c(-100, 200),
                     position="right")+
  scale_x_continuous(labels=scales::label_number(suffix="°",
                                                 accuracy = 1))+
  facet_grid(lockdown.indicator~sub_region_1,
             switch = "y")+
  theme_post()+
  theme(
        axis.title.x = element_text(size = 6,
                                    color="grey30",
                                    hjust=1),
        axis.title.y = element_text(size = 6,
                                    color="grey30",
                                    hjust=1),
        legend.position="bottom",
        strip.text.y = element_text(hjust=1)
  )+
  guides(color=guide_legend(title = "type of days",
                            title.position = "left",
                            direction = "horizontal"))

@@

plot_temp <- df_temp_mobility %>% 
  ggplot()+
    labs(x="daily average temperature",
       y="% change to pre-Covid19 baseline period",
       title="Changes in presences in parks, Covid19 lockdown measures and weather",
       subtitle="Average temperature of state's captial used",
       caption=c("data: NOAA, Google Mobility Reports", "graph: Roland Schmidt | @zoowalk | www.werk.statt.code"))+
  ggbeeswarm:: geom_quasirandom(aes(x=tavg,
                                y=google.value,
                                color=lockdown.indicator),
                                size=.5,
                                groupOnX = T)+
  scale_color_manual(values=c("pre-lockdown"="#008B00",
                              "lockdown"="#EE0000"),
                     name=NULL)+
  scale_y_continuous(labels=scales::label_percent(accuracy = 1,
                                                            scale=1),
                               limits=c(-100, 200),
                     position="right")+
  scale_x_continuous(labels=scales::label_number(suffix="°",
                                                 accuracy = 1))+
  theme_post()+
  theme(
        axis.title.x = element_text(size = 6,
                                    color="grey30",
                                    hjust=1),
        axis.title.y = element_text(size = 6,
                                    color="grey30",
                                    hjust=1),
        legend.position="bottom",
        legend.direction = "horizontal",
        strip.text.y = element_text(hjust=1))+
  lemon::facet_rep_grid(day.indicator~sub_region_1,
                        repeat.tick.labels = T,
                        switch = "y")

>>>>

# Setup
<details closed> 
<summary>Load packages</summary> 
```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(here)
library(extrafont)
loadfonts(device = "win", quiet = T)
library(hrbrthemes)
hrbrthemes::update_geom_font_defaults(family="Roboto Condensed")
# hrbrthemes::update_geom_font_defaults(family="Plex Sans")
library(scales)
library(grid)
library(knitr)
library(geofacet)
library(paletteer)
library(ggtext)
library(glue)
library(gt)

@@

options(width=180, dplyr.width = 150)

plot_bg_color <- readr::read_file(file=here::here("theme.css")) %>% 
  str_extract(., regex("(?<=background-color:).*?(?=;)")) %>% str_trim()

@@

```{r eval=FALSE, fig.height=6, include=FALSE}
plot_park <- df_temp_mobility %>% 
  ggplot()+
  labs(x="daily average temperature",
       y="change to pre-Covid19 baseline period",
       title="Changes in presences in parks, Covid19 lockdown measures and weather",
       subtitle="Average temperature of state's captial used",
       caption=c("data: NOAA, Google Mobility Reports", "graph: Roland Schmidt | @zoowalk | www.werk.statt.code"))+
  geom_smooth(aes(y=google.value,
                  x=tavg),
              size=0.5,
              color="black",
              method='lm', 
              formula= y~x)+
  geom_point(aes(y=google.value,
                 x=tavg,
                 color=day.indicator),
             size=.5)+
  # geom_smooth(aes(y=google.value,
                  # x=tavg))+
  scale_color_manual(values=c("business day"="steelblue",
                                        "public holiday"="green3",
                                        "weekend"="orange"))+
  scale_y_continuous(labels=scales::label_percent(accuracy = 1,
                                                            scale=1),
                               limits=c(-100, 200),
                     position="right")+
  scale_x_continuous(labels=scales::label_number(suffix="°",
                                                 accuracy = 1))+
  facet_grid(lockdown.indicator~sub_region_1,
             switch = "y")+
  theme_post()+
  theme(
        axis.title.x = element_text(size = 6,
                                    color="grey30",
                                    hjust=1),
        axis.title.y = element_text(size = 6,
                                    color="grey30",
                                    hjust=1),
        legend.position="bottom",
        strip.text.y = element_text(hjust=1),
        plot.background = element_rect(fill=plot_bg_color, color=plot_bg_color)
  )+
  guides(color=guide_legend(title = "type of days",
                            title.position = "left",
                            direction = "horizontal"))

@@

plot_temp <- df_temp_mobility %>% 
  ggplot()+
    labs(x="daily average temperature",
       y="% change to pre-Covid19 baseline period",
       title="Changes in presences in parks, Covid19 lockdown measures and weather",
       subtitle="Average temperature of state's captial used",
       caption=c("data: NOAA, Google Mobility Reports", "graph: Roland Schmidt | @zoowalk | www.werk.statt.code"))+
  ggbeeswarm:: geom_quasirandom(aes(x=tavg,
                                y=google.value,
                                color=lockdown.indicator),
                                size=.5,
                                groupOnX = T)+
  scale_color_manual(values=c("pre-lockdown"="#008B00",
                              "lockdown"="#EE0000"),
                     name=NULL)+
  scale_y_continuous(labels=scales::label_percent(accuracy = 1,
                                                            scale=1),
                               limits=c(-100, 200),
                     position="right")+
  scale_x_continuous(labels=scales::label_number(suffix="°",
                                                 accuracy = 1))+
  theme_post()+
  theme(
        axis.title.x = element_text(size = 6,
                                    color="grey30",
                                    hjust=1),
        axis.title.y = element_text(size = 6,
                                    color="grey30",
                                    hjust=1),
        legend.position="bottom",
        legend.direction = "horizontal",
                plot.background = element_rect(fill=plot_bg_color, color=plot_bg_color),
        strip.text.y = element_text(hjust=1))+
  lemon::facet_rep_grid(day.indicator~sub_region_1,
                        repeat.tick.labels = T,
                        switch = "y")
